Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-16 Paper_code-CT_analysis.Rmd
change due to change in CT selection

Here is the code used to have all the values in the pipeline figure

@@

table(all_genes$testis_specificity)
specific_to_pref <- all_genes %>%
  filter(GTEX_category == "testis_specific" |
           multimapping_analysis == "testis_specific") %>% 
  filter(testis_specificity == "testis_preferential")
table(specific_to_pref$not_detected_in_somatic_HPA)
table(specific_to_pref$CCLE_category)
table(specific_to_pref$TCGA_category)

>>>>

Here is the code used to have all the values in the pipeline figure.

As a reminder testis_specificity has been done summarizing testis-specificity 
analysis from GTEX, multimapping, HPA_cell_type_specificities, CCLE and TCGA 
categories.

Testis-specific genes must be: classified as "testis-specific" in GTEX or 
multimappig analysis +  must not be detected in any somatic cell type (in HPA 
scRNAseq analysis) + can not be classified as "leaky" in CLLE and TCGA 
categories + can not be detected (TPM > 0.5) in more than 75% of normal 
peritumoral tissues from a TCGA tumor type.

Testis_preferential genes must be: classified as "testis_preferential" in GTEX 
or multimappig analysis or initially classified as "testis-specific" in GTEX or 
multimappig analysis but downgraded to "testis_preferential because they were 
detected in a somatic cell type (in HPA scRNAseq analysis) + can be detected in 
some somatic cell type but the level has to be at least 10 times lower than the
level detected in a germ cell type (in HPA scRNAseq analysis) must not be 
classified as "leaky" in CLLE and TCGA categories.

@@

table(all_genes$testis_specificity)
table(all_genes$GTEX_category, all_genes$testis_specificity)

specific_to_pref <- all_genes %>%
  filter(GTEX_category == "testis_specific" |
           multimapping_analysis == "testis_specific") %>% 
  filter(testis_specificity == "testis_preferential")
# No more specific to pref as their ratio are all < 10
# all_genes %>%
#   filter(GTEX_category == "testis_specific" |
#            multimapping_analysis == "testis_specific") %>% 
#   filter(!not_detected_in_somatic_HPA)

specific_to_none <- all_genes %>%
  filter(GTEX_category == "testis_specific" |
           multimapping_analysis == "testis_specific") %>% 
  filter(testis_specificity == "not_testis_specific")
table(specific_to_none$CCLE_category)
table(specific_to_none$TCGA_category)
table(specific_to_none$max_q75_in_NT < 0.5)
# 95 lost at this step
table(specific_to_none$not_detected_in_somatic_HPA)
table(specific_to_none$HPA_ratio_germ_som >= 10)

preferential_to_none <- all_genes %>%
  filter(GTEX_category == "testis_preferential" |
           multimapping_analysis == "testis_preferential") %>% 
  filter(testis_specificity == "not_testis_specific")
table(preferential_to_none$CCLE_category)
table(preferential_to_none$TCGA_category)
table(preferential_to_none$not_detected_in_somatic_HPA)
# Almost all detected in somatic
table(preferential_to_none$HPA_ratio_germ_som >= 10)
